\documentclass[11pt]{article}
\usepackage{enumitem}

\renewcommand{\familydefault}{\sfdefault} 

\pagestyle{empty} % Removes page numbers, headers, and footers

\usepackage{titlesec}
\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titlespacing{\section}
{0em}{0em}{0.5em}


%SUBSECTION 
\titleformat{\subsection}[runin]
{\bfseries }
{}
{0em}
{}[:]

\titlespacing{\subsection}
{0em}{0.3em}{0.4em}

\newcommand{\verticalline}[1][1pt]{\rule[-0.35ex]{#1}{0.9em}}

%HEADER
\usepackage{titling}
\usepackage{hyperref}
\renewcommand{\maketitle}{
\begin{center}
    {\huge\bfseries
    \theauthor \hspace{0.5em}{\verticalline[1.5pt]}\hspace{0.5em}Computer Scientist} 

    \vspace{0.7em}

    \ulink{https://orbit-9j.github.io/Portfolio/}{Portfolio} 
    \textbf{$\bullet$  Cardiff, United Kingdom $\bullet$ tianek@protonmail.com  $\bullet$ 07394107227}
\end{center}
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue,
    pdfborder={0 0 0}
}

\usepackage[normalem]{ulem} %underline for links
\newcommand{\ulink}[2]{\href{#1}{\uline{#2}}}

\usepackage[margin=2.3cm]{geometry}
    
\setlength{\parindent}{0pt}

%--------------------------------------CV--------------------------------------
\begin{document}
    \author{Rin Tian}
    \maketitle

    \section{Profile}
    Recent graduate of \textbf{BSc Computer Science} with \textbf{First Cass Honours}, interested in projects that combine \textbf{coding} and \textbf{graphics}. Looking to further develop programming skill set, explore new technical skills, and improve creativity. 

    \begin{center}
        \section{Skills} 
        \subsection{Technical}
    HTML5, CSS3, React JS $\bullet$ Unity 2D, C\# $\bullet$ Python 3, Java $\bullet$ Version Control with Git
        
        \subsection{Soft}
        Presentation $\bullet$ Teamwork $\bullet$ Communication $\bullet$ Time management $\bullet$ Attention to detail $\bullet$ Organisation $\bullet$ Continuous Learning $\bullet$ Creativity
    \end{center}
   
    \section{Recent Projects \& Activities}
    \begin{itemize}[itemsep=0pt, leftmargin=1em]
        \item \ulink{https://orbit-9j.github.io/Portfolio/\#/Cyberscape:\%20a\%20Cybersecurity\%20RPG}{\textbf{Role Playing Game to teach cybersecurity to novices, 05/2023:}} \textbf{Dissertation} project with \textbf{4} game \textbf{levels} covering encryption and phishing concepts, created in \textbf{Unity} engine and coded with \textbf{C\#}. Wrote and followed a 12-week \textbf{time plan}, \textbf{organised} research material using the note taking app \textbf{Obsidian}. Modified \textbf{Creative Commons} assets and \textbf{drew} own assets using \textbf{Krita}. Conducted \textbf{user testing} with \textbf{5 participants} following approval of the university's \textbf{ethics committee}. Scored \textbf{74\%} in the assessment.
        \item \textbf{Flood Management System, 04/2023:} \textbf{Collaborated} with a \textbf{team} of \textbf{5} to design a flood management system for a university-lead \textbf{3-day} \textbf{hackathon}. Used \textbf{Figma} to \textbf{design} a website for the system's user interface as part of the project requirements. Scored group mark of \textbf{80\%} in the assessment.
        \item \ulink{https://orbit-9j.github.io/Portfolio/\#/Psychodyssey}{\textbf{Psychological Horror Game Research and Prototype, 01/2023:}} Conducted a \textbf{survey} with \textbf{19} responses to \textbf{design} an effective psychological horror game that raises awareness of autism. \textbf{Presented} research findings as a poster to class of \textbf{50} students. Laid out research \textbf{findings} on a \textbf{\ulink{https://miro.com/app/board/uXjVPMzhjBo=/?share_link_id=722803847643}{Miro}} board. \textbf{Designed} the game's \textbf{prototype} using \textbf{\ulink{https://www.figma.com/file/pyHXkKKN4cn5MtXx4WpAHR/design-cw?t=gjgzJrZM4Dd0YaZP-1}{Figma}}.  Exchanged \textbf{feedback} with members of a \textbf{team} of \textbf{4} throughout the project to aid in their individual research. Scored \textbf{83\%} in the assessment.
        \item \ulink{https://orbit-9j.github.io/Portfolio/\#/Puzzle\%20Dungeon:\%20a\%20Multiplayer\%20Puzzle\%20Game}{\textbf{Puzzle Dungeon game, 05/2022:}} \textbf{Led} a \textbf{team} of \textbf{3} to meet \textbf{client} requirements for a \textbf{multiplayer} puzzle game over a 2-semester period. Used the \textbf{Unity} game engine with the Mirror \textbf{library} to create the game. Used \textbf{GitLab} to keep track of changes by team members. \textbf{Presented} game progress in 2 client \textbf{meetings}. Scored \textbf{66\%} in the assessment.
        \item \textbf{Science Outreach Leadership Team, 09/2018 – 07/2019:} \textbf{Performed} science demonstrations with liquid nitrogen to \textbf{children} at \textbf{2} \textbf{schools} and multiple \textbf{science festivals} including Blu Dot, Exeter Big Bang, and Big Bang UK in 2019. Checked inventory, set up for shows, and \textbf{memorised} show scripts.
    \end{itemize}
    
    %\section{Work Experience}
    %\begin{itemize}[itemsep=0pt, leftmargin=1em]
         %\item \textbf{Graphic Designer at Praline, London, 06/2017:} \textbf{Designed} \textbf{10} book cover concepts and \textbf{3} accessibility icons for a website using \textbf{Adobe Illustrator}.
    %\end{itemize}

    \section{Education}
    \subsection{Venture Graduates Digital Bootcamp, 09/2023}Learned topics such as UI design, Marketing, Project Management, Digital Communication \& Collaboration 
    \subsection{Cardiff University, Cardiff, 2020-2023} 
    BSc Computer Science with Security and Forensics  \verticalline{} First Class Honours
    \subsection{Badminton School, Bristol, 2015-2020}
    GCSE: 9 A*s, 1 A \verticalline{} A-level: A*AAB
\end{document}